### 2017-08-30 reports/thesis/book.tex
In thesis, added CR bound.

>>>>

The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} from the Fisher's information matrix defined as
\begin{equation}
\matr{I} = -\expectation\left[
\nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
\right] \ .
\end{equation}
The calculation is similar to the derivatives of $T$, so using the same approximations and the that fact $\expectation[Y]=\lambda$, then
\begin{equation}
\matr{I}
=
\begin{pmatrix}
\dfrac{n}{\lambda} & 0 & 0 \\
0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
\end{pmatrix} \ .
\end{equation}
The Cram\'er-Rao lower bound is then
\begin{equation}
\cov\left[
\begin{pmatrix}
\widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
\end{pmatrix}
\right]
= \matr{I}^{-1} \ .
\end{equation}
